Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-04-07 demystify.tex
updates

\paragraph{Tenure-line and teaching faculty} Tenure-line faculty, consisting of tenured and tenured-track profs., focus on research, which includes publishing papers, obtaining grants, and mentoring PhD students.  They often have a low teaching load (e.g., 1 per semester). \emph{Tenured} faculty are professors who have been promoted to a permanent position (informally, very hard to fire them).   \emph{Tenure-track} faculty are (more likely young) professors who are on the track to get tenure.  At most universities, \textbf{only} tenure and tenured track faculty can serve as a formal adviser of PhD students. \autoref{sec:tenure-vs-tenure-track} talks more about choosing between tenure and tenured-track professor as your adviser.

@@

\emph{Research faculty} or research scientists are typically non-tenure line faculty who focus on research (e.g., publishing papers and getting grants). While they cannot serve as a formal adviser, they often co-advise and mentor students with tenure-line faculty. They can recruit students and provide RA funding for them.

>>>>

\paragraph{Tenure-line and teaching faculty} Tenure-line faculty, consisting of tenured and tenured-track profs., focus on research, which includes publishing papers, obtaining grants, and mentoring PhD students.  They often have a low teaching load (e.g., 1 per semester). \emph{Tenured} faculty are professors who have been promoted to a permanent position (informally, very hard to fire them).   \emph{Tenure-track} faculty are (more likely young) professors who are on the track to get tenure.  At most universities, \textbf{only tenure and tenured track} faculty can serve as a formal adviser of PhD students. \autoref{sec:tenure-vs-tenure-track} talks more about choosing between tenure and tenured-track professor as your adviser.

@@

Some universities have \emph{research faculty} or research scientists, who are typically non-tenure line faculty who focus on research (e.g., publishing papers and getting grants). While they cannot solely graduate PhD students, they often co-advise and mentor students with tenure-line faculty. They can recruit students and provide RA funding for them.
